Gozde and Liora Replication Code

### 2015-04-07 Gozde-Liora-Replication-Code.Rmd
updated code
replication final commit
Test for pushing problems

---
title: "Gozde and Liora Replication Code"
author: "Gozde Guran and Liora Goldensher"
date: "3/6/2015"
output: html_document
---

# Replication Code for "Contextual Factors and the Extreme Right Vote in Europe, 1980-2002" by Kai Arzheimer American Journal of Political Science (2009)

Note: Please refer to saved files in our repository for images from the article. Also please refer to the table and figures (Table 1, Figure 1, 2) in the repository. Image scales are rearranged in saved versions. Our regression values are slightly different from the authors as his stata code used a slightly different method than our function (glmmPQL) to calculate Penalized Quasi-likehood. Finally, we were not able to reproduce the last two figures that showed the joint impact of more than 2 variables.

@@

# Second part of Figure 2

>>>>

---
title: "Gozde and Liora Replication Code"
author: "Gozde Guran and Liora Goldensher"
date: "3/6/2015"
output: html_document
---
test
# Replication Code for "Contextual Factors and the Extreme Right Vote in Europe, 1980-2002" by Kai Arzheimer American Journal of Political Science (2009)

Note: Please refer to saved files in our repository for images from the article. Also please refer to the table and figures (Table 1, Figure 1, 2) in the repository. Image scales are rearranged in saved versions. Our regression values are slightly different from the authors as his stata code used a slightly different method than our function (glmmPQL) to calculate Penalized Quasi-likehood. Finally, we were not able to reproduce the last two figures that showed the joint impact of more than 2 variables; we'll keep working on these.

@@

# Second part of Figure 2:
